Estimation below the detection limit

### 2018-04-12 TEX/draft2.tex
Soem changes to wording

The minimal order of data statistics used to get an accurate estimation of a signal is important to understand, in the asymptotic $\SNR$ regime, the sample complexity of the problem.
In methods which are based on detection and averaging, the number of signals occurrences  must scale like $\sigma^2$. Taking the $d$th order autocorrelation function amplifies the variance of the noise by a factor of $d$. Therefore, the required number signal occurrences should scale like $\sigma^{2d}$  to retain some constant estimation error. Accordingly, in our  method, $M$ must scale like $\sigma^6$. In Section~\ref{sec:numerics}, we show empirically the third-order autocorrelation suffices also for a mixture of $K>1$ signals without prior knowledge of the $M_i$'s and $\sigma$.  \TODO{question mark on the entire paragraph}

@@

Given the observation $y$, we proceed to compute the moments. The first-order moment is straightforward. For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$. Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments. Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements. As a result, it is unnecessary to estimate $\sigma$. In practice, the moments are computed on batches of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points. Batches are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.

>>>>

The minimal order of data statistics used to get an accurate estimation of a signal is important to understand, in the asymptotic $\SNR$ regime, the sample complexity of the problem.
In methods which are based on detection and averaging, the number of signals occurrences  must scale like $\sigma^2$. Taking the $d$th order autocorrelation function amplifies the variance of the noise by a factor of $d$. Therefore, the required number signal occurrences should scale like $\sigma^{2d}$  to retain some constant estimation error. Accordingly, in our  method, $M$ must scale like $\sigma^6$. In Section~\ref{sec:numerics}, we show empirically the third-order autocorrelation suffices also for a mixture of $K>1$ signals without prior knowledge of the $M_i$'s and $\sigma$.  \TODO{question mark on the entire paragraph}
\TODO{We could move here the paragraphs from 1D XP about which moments we compute, to argue that we can expect to recover at most up to $K = L/2$ signals.}

@@

Given the observation $y$, we proceed to compute the moments. The first-order moment is straightforward. For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$. Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments. Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements---there are $\frac{(L-1)(L-2)}{2}$ such moments. As a result, it is unnecessary to estimate $\sigma$. There are
\begin{align*}
	1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
\end{align*}
moments in total. In practice, these are computed on disjoint segments of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points. Segments are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
